COG-ED Manuscript

### 2022-02-14 06_Paper/COG-ED/Manuscript.Rmd
Update Manuscript.Rmd

With he present study, we change <!-- in my opinion better: alter --> one fundamental assumption of the original COG-ED paradigm: That the easiest *n*-back level has the highest SV.
We therfore adapted the COG-ED paradigm in such a way that it allows the computation of SVs for different *n*-back levels without presuming that all individuals inherently prefer the easiest level.
Figure\ 1 illustrates how different modifications of the COG-ED paradigm return SVs that do or do not reflect the true preference of a hypothetical participant, who likes 2-back most, 3-back less, and 1-back least.
The COG-ED paradigm sets the SV of 1-back to 1, regardless of the response pattern.
Adding a comparison of 2-back and 3-back allows the SVs of those two levels to be more differentiated, but leaves the SV of 1-back unchanged.
Adding three more comparisons of the same levels but using the easier level as reference does approach the true preference, but has two disadvantages.
First, the SVs are still distorted by the SVs returned by the original paradigm, and second, having more task levels would lead to an exponential increase in comparisons.
Therefore, the solution lies in reducing the number of necessary comparisons by presenting only one ED round for each possible pair of levels, and by starting each round with a choice between equal prices.
For example, the participant is presented with the choice of receiving 1€ for 2-back or 1€ for 4-back.
The level chosen by the participant will then be used as the level with a flexible value, which starts at 1€ and is changed in every iteration.
The level that was not chosen will be set to a fixed value of 2€.
This procedure allows to compute SVs based on actual individual preference instead of objective task load.
Each level's SV is calculated as the mean of this level's SVs from all comparisons in which it appeared.
If the participant has a clear preference for one level, this level's SV will be 1.
If not, then no level's SV will be 1, but each level's SV can still be interpreted as an absolute and relative value, so each participant's ED behaviour can still be quantified.
Since we also aim to establish this paradigm for the assessment of tasks with no objective task load, e.g., emotion regulation tasks <!-- perhaps add ref. to the other ms. on this issue? -->, we call it the Cognitive and Emotion Regulation Effort Discounting Paradigm (CERED). <!-- not sure whether you should call it like this; while it reflects the so-called "Entstehungszusammenhang", it does not necessarily reflect the so-called "Begründungszusammenhang", i.e., the proposed approach goes beyond emotion regulation, but applies to  
In the present study, we will validate the CERED paradigm by conceptually replicating the findings of Westbrook et al. [-@Westbrook2013].
Additionally, we will compare the ED behaviour of participants regarding the *n*-back task and an emotion regulation task.
The full results of the latter will be published in a second Registered Report<!-- again: add (interim) ref. -->.
The COG-ED paradigm has been applied to tasks in different domains before, showing that SVs across task domains correlate [@Crawford2021], but these tasks had an objective order of task load, which is not the case for the choice of emotion regulation strategies or other paradigms where there is no objective order of task load.

>>>>

With the present study, we change <!-- in my opinion better: alter --> one fundamental assumption of the original COG-ED paradigm: That the easiest *n*-back level has the highest SV.
We therfore adapted the COG-ED paradigm in such a way that it allows the computation of SVs for different *n*-back levels without presuming that all individuals inherently prefer the easiest level.
Figure\ 1 illustrates how different modifications of the COG-ED paradigm return SVs that do or do not reflect the true preference of a hypothetical participant, who likes 2-back most, 3-back less, and 1-back least.
The COG-ED paradigm sets the SV of 1-back to 1, regardless of the response pattern.
Adding a comparison of 2-back and 3-back allows the SVs of those two levels to be more differentiated, but leaves the SV of 1-back unchanged.
Adding three more comparisons of the same levels but using the easier level as reference does approach the true preference, but has two disadvantages.
First, the SVs are still distorted by the SVs returned by the original paradigm, and second, having more task levels would lead to an exponential increase in comparisons.
Therefore, the solution lies in reducing the number of necessary comparisons by presenting only one ED round for each possible pair of levels, and by starting each round with a choice between equal prices.
For example, the participant is presented with the choice of receiving 1€ for 2-back or 1€ for 4-back.
The level chosen by the participant will then be used as the level with a flexible value, which starts at 1€ and is changed in every iteration.
The level that was not chosen will be set to a fixed value of 2€.
This procedure allows to compute SVs based on actual individual preference instead of objective task load.
Each level's SV is calculated as the mean of this level's SVs from all comparisons in which it appeared.
If the participant has a clear preference for one level, this level's SV will be 1.
If not, then no level's SV will be 1, but each level's SV can still be interpreted as an absolute and relative value, so each participant's ED behaviour can still be quantified.
Since we also aim to establish this paradigm for the assessment of tasks with no objective task load, e.g., emotion regulation tasks <!-- perhaps add ref. to the other ms. on this issue? -->, we call it the Cognitive and Emotion Regulation Effort Discounting Paradigm (CERED). <!-- not sure whether you should call it like this; while it reflects the so-called "Entstehungszusammenhang", it does not necessarily reflect the so-called "Begründungszusammenhang", i.e., the proposed approach goes beyond emotion regulation, but applies to  
In the present study, we will validate the CERED paradigm by conceptually replicating the findings of Westbrook et al. [-@Westbrook2013].
Additionally, we will compare the ED behaviour of participants regarding the *n*-back task and an emotion regulation task.
The full results of the latter will be published in a second Registered Report<!-- again: add (interim) ref. -->.
The COG-ED paradigm has been applied to tasks in different domains before, showing that SVs across task domains correlate [@Crawford2021], but these tasks had an objective order of task load, which is not the case for the choice of emotion regulation strategies or other paradigms where there is no objective order of task load.
